Validation of Visual Statistical Inference, Applied to Linear Models (supplementary materials)

### 2013-04-18 supplementary.tex
final versions

The materials in this document supplement the information presented in the manuscript ``Validation of Visual Statistical Inference, Applied to Linear Models".  Section \ref{sec:lineup_selection} describes how the lineups are presented to the subjects for evaluation, section \ref{sec:proof_lemma} presents the proof of the Lemma \ref{p-lemma} in the manuscript. The detailed discussion on how much the choice of null plots affect is included in Section \ref{sec:null_choice} which supplement the information in Section \ref{p-sec:null_choice} of the manuscript. Section \ref{sec:typeIII_error} includes the detailed discussion about the Type-III error supplementing Section  \ref{p-sec:typeIII_error}. The data cleaning process and how that may affect the result are discussed in Section \ref{sec:data_cleaning} which supplements Section \ref{p-sec:data_cleaning} of the manuscript.

>>>>

The materials in this document supplement the information presented in the manuscript ``Validation of Visual Statistical Inference, Applied to Linear Models''. Section \ref{sec:proof_lemma} presents the proof of the Lemma \ref{p-lemma} in the manuscript. Section \ref{sec:lineup_selection} describes how the lineups are presented to the subjects for evaluation.  The data cleaning process and how that may affect the result are discussed in Section \ref{sec:data_cleaning} which supplements Section \ref{p-sec:data_cleaning} of the manuscript. The detailed discussion on how much the choice of null plots affect is included in Section \ref{sec:null_choice} which supplement the information in Section \ref{p-sec:null_choice} of the manuscript. Section \ref{sec:typeIII_error} includes the detailed discussion about the Type-III error supplementing Section  \ref{p-sec:typeIII_error}.
